---
output: 
  pdf_document:
    pandoc_args: "--highlight-style=files/mcshanepdf.theme"
    latex_engine: lualatex        # Only needed for custom fonts
header-includes: 
 - \newcommand{\lecture}{Dr. McShane}
 - \newcommand{\scribe}{Sunny Lin}
 - \newcommand{\chtitle}{Final Project Proposal}
 - \newcommand{\lecdate}{Due April 23rd at 10pm}
 - \definecolor{codegray}{HTML}{f9f9f9}
 - \definecolor{codeletter}{HTML}{002c6b}
 - \let\textttOrig\texttt
 - \renewcommand{\texttt}[1]{\textttOrig{\textbf{\textcolor{codeletter}{\colorbox{codegray}{#1}}}}}
 - \usepackage{fontspec}          # Only needed for custom fonts
 - \setmainfont{Jost-Regular}[Extension=.ttf,Path=files/,BoldFont=Jost-Bold,ItalicFont=Jost-Italic,BoldItalicFont=Jost-BoldItalic]
csl: files/ASA-McShane.csl
urlcolor: blue
linestretch: 1
---

```{r include = FALSE}
hook_chunk = knitr::knit_hooks$get('chunk')
ls.flag = rmarkdown::metadata$linestretch
ls.flag = ifelse(is.null(ls.flag), TRUE, ls.flag != 1.5)

if (!ls.flag){
knitr::knit_hooks$set(chunk = function(x, options) {
  regular_output = hook_chunk(x, options)
  # add latex commands if chunk option singlespacing is TRUE
  if (isTRUE(options$singlespacing)) sprintf("\\setstretch{1} \\small \n %s \n \\setstretch{1.5} \\normalsize", regular_output)
  else regular_output
})}

knitr::opts_chunk$set(   # This is for later! Don't worry about it now. 
  echo = FALSE,          # Don't show code.
  warning = FALSE,       # Don't show warnings.
  message = FALSE,       # Don't show messages (less serious warnings).
  fig.align = "center",  # Center figures.
  fig.width = 5,         # Size figures nicely by default
  fig.height = 3,        # Size figures nicely by default
  dev = "cairo_pdf",     # Enable this to use custom fonts
  singlespacing = TRUE   # Makes code single spaced and returns to 1.5
)
library(tidyverse)       # Load libraries you always use here.
library(kableExtra)
library(cowplot)
library(jsonlite)
# library(rjson)

set.seed(18)             # Make random results reproducible
theme_set(theme_bw())    # Uses clean ggplot2 theme
```

<!-- Don't delete this -->
\rule{6.5in}{2pt}
\large \textbf{STAT375: Statistical Aspects of Competition \hfill with \lecture}

\textbf{\chtitle \hfill \lecdate \hfill \scribe} \normalsize
\rule{6.5in}{2pt}
<!-- Don't delete this -->


# Context

**Which sport, game, etc will you be analyzing?**
\newline
I will be analyzing basketball. 


# Overall Proposal

**What do you propose to do?**
\newline
I will be looking at tracking data to determine where players of the defensive team are when they miss a shot attempt and it is a turnover (how far players are from the basket) and how that affects the next possession (whether they get "back on defense" faster). I would like to examine if player position has a significant effect on next possession as well as the outcome of the game overall (W/L). If applicable, I'd also like to examine how the position of offensive players affects turnover vs offensive rebounds ratio on their offensive attempt.

# Data

**What data do you plan to use? (Provide a link to the page or pages where this is contained or described). Scrape/read-in the data here. Describe the origin of the data, who collected it, how large is it (# rows, columns, tables, file size, etc as appropriate)?**

```{r}
# #run once to put data into R
# #data can be found in data.zip from Github to get two .json files
# source("_functions.R")
# 
# #tried the exact data that he used in the specific webpage: still NAs
# #http://projects.rajivshah.com/sportvu/EDA_NBA_SportVu.html
# all.movements <- sportvu_convert_json(file = "0021500001.json")
# 
# #a random file (01.02.2016.DEN.at.GSW.7z) taken from 
# #https://github.com/rajshah4/BasketballData/tree/master/2016.NBA.Raw.SportVU.Game.Logs
# # still has NAs
# all.movements.2 <- sportvu_convert_json(file = "0021500504.json")
# #result <- rjson::fromJSON(file = "0021500504.json")
```

```{r}
# # Trying to take a look at the json file 
# df <- result$events[[1]]$moments
```






# Exploratory Data Analysis

**Explore your data with `ggpairs` or as you think is appropriate. If using `ggpairs`, no more than 6 variables should be included at a time. `ggduo` can be used to fill in the "off-diagonal" pairs in an overall scatterplot matrix. If you have too many columns (say, over 18) to make this meaningful, select at least 12 columns to explore, including your candidate response variable or variables. This does not need to be submitted as part of your proposal, but you'll need to do this eventually (if your project is based on data).** 



# Methods

**What statistical methods will you be using? (Simulation counts). Will you be assessing models by technique?**



# US-RESP or US-CLAP

**Which competition would your project be eligible for, do you think? If US-CLAP, describe which course you've seen the method in. If US-RESP, confirm that you have not taken a class that has covered that topic.**



# Number of group members

**To adequately address this problem, how many people do you think would be needed in a group to address it? (1 to 3 group members is feasible, but again, additional people means the scope of the project needs to expand.)**
\newline 
1-3 people all work for me.


# Would you be willing to join someone else's project? 

Yes, I believe I am working with Sean Dube. 


**Submit this on Gradescope, individually, by Friday at 10pm**






<!-- don't delete and don't write below this line -->
<!-- \newpage -->
<!-- # References -->

`r ifelse(!ls.flag, yes = sprintf("\\setstretch{1}"), no = "")`

